\documentclass[11pt,a4paper]{article}
\usepackage{cv_preamble}
\usepackage{personal_info}

\begin{document}

{\bf \Huge \color{myblue} Harry Lanz - MEng, PhD}

\begin{tblr}{
  colspec = {l l X r r},
  width = \linewidth,
  rows = {rowsep=0pt},
  leftsep = 0pt,
  rightsep = 0pt
}
\textbf{Email:}    & \email & & \textbf{LinkedIn:} & \linkedin \\
\textbf{Tel:}      & \tel   & & \textbf{GitHub:}   & \github
\end{tblr}

\vspace{0.2cm}\hrule
{\bf Backend Software Engineer with experience building production-grade systems and data pipelines. Strong fundamentals in Go, Python, \cpp, Linux, and Docker. Product-minded, comfortable with ambiguity, and experienced owning systems end-to-end.} \\ \vspace{-0.2cm} \hrule

\section*{Experience}
\hrule

\textbf{PhD:}

\begin{itemize}
  \item Primary engineer responsible for the design, implementation, and long-term maintenance of multiple production software systems.
  \item Owned and evolved a production-grade backend software stack (Python, \cpp) supporting a custom MRI platform used daily by researchers and clinicians.
  \item Reduced end-to-end data processing latency by a factor of 10, transforming an offline batch workflow into an interactive, user-facing analysis tool.
  \item Replaced multiple manual pipeline stages with fully automated, fault-tolerant implementations, directly enabling first-in-human testing with surgical correlation of results.
  \item Designed and maintained data pipelines processing large 3D datasets with strict correctness, performance, and reproducibility requirements.
  \item Built long-running services for hardware coordination, including state machines, structured logging, validation checks, and defensive error handling.
  \item Acted as the primary point of contact for debugging, failure investigation, and behavioural changes in production systems.
  \item Collaborated closely with non-engineering stakeholders to translate ambiguous requirements into robust technical solutions.
  \item Mentored and onboarded Master's students contributing to production codebases, providing design guidance, code reviews, and debugging support.

  
  
  % \item Owned the full lifecycle of multiple medium-sized software systems, from initial design through deployment, iteration, and long-term support.
  % \item Acted as the primary point of contact for debugging, failure investigation, and behavioural changes in production systems.
  % \item Collaborated closely with non-engineering stakeholders to translate ambiguous requirements into robust technical solutions.
  % \item Designed data pipelines processing large 3D datasets with strict correctness, performance, and reproducibility requirements.
  % \item Built long-running services for hardware coordination, including state machines, fault handling, structured logging, and safety interlocks.
  % \item Made trade-offs between performance, complexity, and usability in collaboration with non-engineering stakeholders.
  % \item Designed multi-process systems resilient to partial failure, including retry logic, idempotent operations, and observable execution paths.
  % \item Reduced data processing latency by a factor of 10, transforming a batch workflow into an interactive system integrated directly into a user-facing analysis tool.
  % \item Replaced multiple manual pipeline stages with fully automated, fault-tolerant implementations, enabling first-in-human testing of a new MRI scanner with surgical correlation of results.
  % \item Improved system reliability through structured logging, validation checks, and defensive error handling, reducing failure rates during routine use.
  % \item Mentored and onboarded Master's students contributing to production codebases, including design guidance, code reviews, and debugging support.
\end{itemize}

\textbf{Master's project:}

\begin{itemize}
  \item Extended a large Fortran-based CFD codebase to support new numerical analysis methods for identifying chaotic turbulent flow regions.
  \item Worked within an existing production codebase, adding functionality without breaking established workflows.
\end{itemize}

\textbf{Aeronautics high performance computing:}

\begin{itemize}
  \item Implemented a parallel \cpp solver for fluid dynamics simulations using domain decomposition and deployed it on a shared HPC cluster environment using MPI.
\end{itemize}

\textbf{Mindbridge:}

\begin{itemize}
  \item Developed a Python-based data ingestion tool to digitise handwritten questionnaire responses from scanned documents into a CSV.
  \item Built a PyQt GUI workflow enabling human validation of ambiguous entries before export to CSV for downstream analysis.
\end{itemize}

\textbf{Personal Projects:}

\begin{itemize}
  \item Designed embedded \cpp applications on ESP32 involving networked device control over TCP/IP and REST interfaces; implemented request handling, state management, and failure recovery.
  \item Experience operating Linux services on Raspberry Pi including VPN, DNS, and media servers, deployed using Docker and Docker Compose; configured networking, port forwarding, and service isolation.
\end{itemize}
  

\section*{Education}
\hrule

\textbf{PhD Mechanical Engineering}, Imperial College London \hfill [2020--2025]\\PhD awarded; viva passed November 2025

\textbf{MEng Aeronautics} (Integrated Masters), Imperial College London \hfill [2015--2020]\\First class honours; Dean's List (Master's year)



\section*{Skills}
\hrule

\textbf{Programming languages:} Go, Python, \cpp, SQL, Bash

\textbf{Backend \& systems:} Linux, Docker, RESTful services, concurrency, service reliability and observability, basic networking

\textbf{Developer tooling:} Git, GitHub, CI/CD (GitHub Actions), VS Code, Neovim, pytest

\textbf{Data \& scientific computing:} NumPy, SciPy, PyTorch, MATLAB, Fortran

\textbf{GUI \& desktop:} Qt, PyQt

\section*{Selected research output}
\hrule

\textbf{First In Vivo Magic Angle Directional Imaging Using Dedicated Low-Field MRI} \hfill [2025]\\
\textit{Published in the Journal of Magnetic Resonance in Medicine:} \href{https://doi.org/10.1002/mrm.30332}{doi.org/10.1002/mrm.30332}

\begin{itemize}
  \item Designed and maintained a production software platform used by multiple researchers, prioritising correctness, usability, and long-term maintainability.
\end{itemize}

\section*{Other experience}
\hrule

\begin{itemize}
  \item Supplementary software engineering training (Boot.dev - Python, Go, Linux, SQL, Docker).
  \item Supervised Master's students on Python-based image reconstruction and performed code reviews.
\end{itemize}


References are available upon request.



\end{document}